### 2014-11-03 Projects/DelCo_2012/Report/DelCo_2012.tex
DelCo 2012: New Figures (floor plan, instrumentation) and Inserted into Report
DelCo 2012: New Fuel Load Drawings
DelCo 2012: Report Re-structuring and addition of burn building figures.

@@

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

\subsection{Burn Building - Gas Cooling}
\label{sec:Burn_Building}

\subsection{Concrete Structures - Fire Suppression}
\label{sec:Experimental Structures}

@@

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/DelCoSingleStoryDimensionsMetric}
	\caption{Floor Plan of the Test Structure.}
	\label{fig:Test_Structure_Floor_Plan}
\end{figure}

@@

\subsection{Gas Cooling Instrumentation}
\label{subsec:Gas_Cooling_Instrumentation}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/DelCoBurnBuildingInstrumentation}
	\caption{Photograph of the Instrumentation Dimensions in the Gas Cooling Experiments}
	\label{fig:Gas_Cooling_Instrumentation_Dimensions}
\end{figure}

\subsection{Fire Suppression Instrumentation}
\label{subsec:Fire_Suppression_Instrumentation}

@@

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/DelCoSingleStoryInstrumentationDimensions}
	\caption{Photograph of the Instrumentation Dimensions in the Fire Suppression Experiments.}
	\label{fig:Fire_Suppression_Instrumentation_Dimensions}
\end{figure}

@@

\subsubsection{Gas Cooling Experiments}
\label{subsubsec:Gas_Cooling_Temperature_Instrumentation}

\subsubsection{Fire Suppression Experiments}
\label{subsubsec:Fire_Suppression_Temperature_Instrumentation}

@@

\subsubsection{Gas Cooling Experiments}
\label{subsubsec:Gas_Cooling_Heat_Flux_Instrumentation}

\subsubsection{Fire Suppression Experiments}
\label{subsubsec:Fire_Suppression_Heat_Flux_Instrumentation}

@@

\subsubsection{Gas Cooling Experiments}
\label{subsubsec:Gas_Cooling_Gas_Velocity_Instrumentation}

\subsubsection{Fire Suppression Experiments}
\label{subsubsec:Fire_Suppression_Gas_Velocity_Instrumentation}

@@

\section{Fuel Load: Gas Cooling}
\label{sec:Fuel_Load:_Gas_Cooling}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/DelCoBurnBuildingFuelLoad}
	\caption{Burn Building Fuel Load.}
	\label{fig:Burn_Building_Fuel_Load}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/DelCoSingleStoryWoodFuelLoad}
	\caption{Wood Fuel Load Dimensions.}
	\label{fig:Wood_Fuel_Load_Dimensions}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/DelCoSingleStoryFurnitureFuelLoad}
	\caption{Furniture Fuel Load Dimensions.}
	\label{fig:Furniture_Fuel_Load_Dimensions}
\end{figure}
